Radio Telescope Observations Of The April 8, 2024 Total Solar Eclipse At 1420MHz.

### 2025-03-06 sections/observations.tex
Explained why we need to compare the optical and radio lightcurve in the intro to the optical section

As a comparison to the radio lightcurve created in the previous section, we have 3 sources of optical lightcurve data: A livestream lightcurve using a solar filter-equipped optical telescope, a Vernier Light Sensor (LS-BTA) pointed straight up at the sky, and a theoretical lightcurve created using the software Stellarum.

>>>>

We collected optical lightcurve data to compare contact times, the depth of the eclipse, and the shape of the lightcurve to our radio observations. Our two sources include a livestream lightcurve using a solar filter-equipped optical telescope, and a Vernier Light Sensor (LS-BTA) pointed straight up at the sky.
